Modern BTree\\ techniques

### 2019-12-31 btree/presentation.tex
Base btree diagram

\tikzset{rum-node/.style={draw,circle,fill=white,minimum width=2cm}}
\tikzset{rum-extra-node/.style={rectangle, draw, dashed, rounded corners, fill=white }}

@@

    \begin{tikzpicture}[]
        \path
          node[minimum height=1cm, draw] (pointer1) {}
          node[minimum height=1cm, pattern=north west lines, draw, right=0 of pointer1] (sep1) {}
          node[minimum height=1cm, pattern=north west lines, draw, left=0 of pointer1] (sep2) {}
          node[minimum height=1cm, draw, right=0 of sep1] (pointer2) {}
          node[minimum height=1cm, draw, left=0 of sep2] (pointer3) {}
          node[minimum height=1cm, pattern=north west lines, draw, right=0 of pointer2] (sep3) {}
          node[minimum height=1cm, pattern=north west lines, draw, left=0 of pointer3] (sep4) {}
          node[draw, inner sep=0, behind path,
              fit=(pointer1)(pointer2)(pointer3)
                  (sep1)(sep2)(sep3)(sep4)
          ] (root) {};

        \path
          node[minimum height=0.5cm, pattern=north west lines, draw, below=1cm of root] (key11) {}
          node[minimum height=0.5cm, pattern=north west lines, draw, left=0 of key11] (key21) {}
          node[minimum height=0.5cm, pattern=north west lines, draw, right=0 of key11] (key31) {}
          node[minimum height=0.5cm, draw, below=0 of key11] (val11) {}
          node[minimum height=0.5cm, draw, left=0 of val11] (val21) {}
          node[minimum height=0.5cm, draw, right=0 of val11] (val31) {}
          node[draw, inner sep=0, behind path,
              fit=(key11)(key21)(key31)
                  (val11)(val21)(val31)
          ] (child1) {};

        \path
          node[minimum height=0.5cm, pattern=north west lines, draw, below=1cm of root.south west, xshift=-2cm] (key12) {}
          node[minimum height=0.5cm, pattern=north west lines, draw, left=0 of key12] (key22) {}
          node[minimum height=0.5cm, pattern=north west lines, draw, right=0 of key12] (key32) {}
          node[minimum height=0.5cm, draw, below=0 of key12] (val12) {}
          node[minimum height=0.5cm, draw, left=0 of val12] (val22) {}
          node[minimum height=0.5cm, draw, right=0 of val12] (val32) {}
          node[draw, inner sep=0, behind path,
              fit=(key12)(key22)(key32)
                  (val12)(val22)(val32)
          ] (child2) {};

        \path
          node[minimum height=0.5cm, pattern=north west lines, draw, below=1cm of root.south east, xshift=2cm] (key13) {}
          node[minimum height=0.5cm, pattern=north west lines, draw, left=0 of key13] (key23) {}
          node[minimum height=0.5cm, pattern=north west lines, draw, right=0 of key13] (key33) {}
          node[minimum height=0.5cm, draw, below=0 of key13] (val13) {}
          node[minimum height=0.5cm, draw, left=0 of val13] (val23) {}
          node[minimum height=0.5cm, draw, right=0 of val13] (val33) {}
          node[draw, inner sep=0, behind path,
              fit=(key13)(key23)(key33)
                  (val13)(val23)(val33)
          ] (child3) {};

        \draw[->] (pointer1.south) -- (key11.north);
        \draw[->] (pointer2.south) .. controls ([yshift=-1cm] pointer2) and ([yshift=1cm] key13) .. (key13.north);
        \draw[->] (pointer3.south) .. controls ([yshift=-1cm] pointer3) and ([yshift=1cm] key12) .. (key12.north);
    \end{tikzpicture}

>>>>

\tikzset{rum-node/.style={draw,circle,fill=white,minimum width=2cm}}
\tikzset{rum-extra-node/.style={rectangle, draw, dashed, rounded corners, fill=white }}
\tikzset{btree-key/.style={minimum height=1cm, pattern=north west lines, draw}}
\tikzset{btree-pointer/.style={minimum height=1cm, draw}}
\tikzset{btree-hide/.style={draw opacity=0, line width=0, pattern=none}}
\tikzset{btree-leaf/.style={fill=greenGood}}
\tikzset{btree-branch/.style={fill=gray!20}}
\tikzset{btree-line/.style={line width=0.5pt}}
\tikzset{btree-path/.style={btree-pointer, minimum width=0.8cm, fill=red, opacity=0.5}}
\tikzset{>=latex}

\newcommand{\btreenode}[5] {
    \path
      node[btree-pointer, #2, #3] (pointer1#1) {}
      node[btree-key, right=0 of pointer1#1, #3] (sep1#1) {}
      node[btree-key, left=0 of pointer1#1, #3] (sep2#1) {}
      node[btree-pointer, right=0 of sep1#1, #3] (pointer2#1) {}
      node[btree-pointer, left=0 of sep2#1, #3] (pointer3#1) {}
      node[btree-key, right=0 of pointer2#1, #3] (sep3#1) {}
      node[btree-key, left=0 of pointer3#1, #3] (sep4#1) {}
      node[draw, inner sep=0, behind path, #4,
          fit=(pointer1#1)(pointer2#1)(pointer3#1)
              (sep1#1)(sep2#1)(sep3#1)(sep4#1)
      ] (node#1) {};

      \ifthenelse{ \equal{#5}{show-pointers} } {
            \coordinate[below=0.5 of pointer1#1] (heap-pointer1#1);
            \coordinate[below=0.5 of pointer2#1] (heap-pointer2#1);
            \coordinate[below=0.5 of pointer3#1] (heap-pointer3#1);

            \draw[->, btree-line] (pointer1#1.south) -- (heap-pointer1#1.north);
            \draw[->, btree-line] (pointer2#1.south) -- (heap-pointer2#1.north);
            \draw[->, btree-line] (pointer3#1.south) -- (heap-pointer3#1.north);
      } {}
}

@@

    \begin{center}
    \begin{overprint}[12cm]
        \onslide<1>
        \begin{tikzpicture}[]
            \btreenode{1}{}{btree-hide}{}{}
            \btreenode{2}{below=1cm of node1.south}{btree-hide}{}{}
            \btreenode{3}{below=1cm of node1.south west, xshift=-3cm}{btree-hide}{}{}
            \btreenode{4}{below=1cm of node1.south east, xshift=3cm}{btree-hide}{}{}

            \draw[->, btree-line] (pointer11.south) -- (pointer12.north);
            \draw[->, btree-line] (pointer21.south)
                .. controls ([yshift=-1cm] pointer21) and ([yshift=1cm] pointer14) ..
                (pointer14.north);
            \draw[->, btree-line] (pointer31.south)
                .. controls ([yshift=-1cm] pointer31) and ([yshift=1cm] pointer13) ..
                (pointer13.north);
        \end{tikzpicture}

        \onslide<2>
        \begin{tikzpicture}[]
            \btreenode{1}{}{btree-hide}{btree-branch}{}
            \btreenode{2}{below=1cm of node1.south}{btree-hide}{btree-leaf}{}
            \btreenode{3}{below=1cm of node1.south west, xshift=-3cm}{btree-hide}{btree-leaf}{}
            \btreenode{4}{below=1cm of node1.south east, xshift=3cm}{btree-hide}{btree-leaf}{}

            \draw[->, btree-line] (pointer11.south) -- (pointer12.north);
            \draw[->, btree-line] (pointer21.south)
                .. controls ([yshift=-1cm] pointer21) and ([yshift=1cm] pointer14) ..
                (pointer14.north);
            \draw[->, btree-line] (pointer31.south)
            .. controls ([yshift=-1cm] pointer31) and ([yshift=1cm] pointer13) ..
            (pointer13.north);
        \end{tikzpicture}

        \onslide<3>
        \begin{tikzpicture}[]
            \btreenode{1}{}{}{btree-branch}{}
            \btreenode{2}{below=1cm of node1.south}
                {}{btree-leaf}{show-pointers}
            \btreenode{3}{below=1cm of node1.south west, xshift=-3cm}
                {}{btree-leaf}{show-pointers}
            \btreenode{4}{below=1cm of node1.south east, xshift=3cm}
                {}{btree-leaf}{show-pointers}

            \draw[->, btree-line] (pointer11.south) -- (pointer12.north);
            \draw[->, btree-line] (pointer21.south)
                .. controls ([yshift=-1cm] pointer21) and ([yshift=1cm] pointer14) ..
                (pointer14.north);
            \draw[->, btree-line] (pointer31.south)
                .. controls ([yshift=-1cm] pointer31) and ([yshift=1cm] pointer13) ..
                (pointer13.north);
        \end{tikzpicture}

        \onslide<4>
        \begin{tikzpicture}[]
            \btreenode{1}{}{}{btree-branch}{}
            \btreenode{2}{below=1cm of node1.south}
                {}{btree-leaf}{show-pointers}
            \btreenode{3}{below=1cm of node1.south west, xshift=-3cm}
                {}{btree-leaf}{show-pointers}
            \btreenode{4}{below=1cm of node1.south east, xshift=3cm}
                {}{btree-leaf}{show-pointers}

            \draw[->, btree-line, color=red, line width=2pt] (pointer11.south) -- (pointer12.north);
            \draw[->, btree-line] (pointer21.south)
                .. controls ([yshift=-1cm] pointer21) and ([yshift=1cm] pointer14) ..
                (pointer14.north);
            \draw[->, btree-line] (pointer31.south)
                .. controls ([yshift=-1cm] pointer31) and ([yshift=1cm] pointer13)
                .. (pointer13.north);

            \path
              node[btree-path, below=-0.505 of pointer11.west] (path-pointer1) {}
              node[btree-path, below=-0.505 of pointer32.west] (path-pointer2) {};

            \draw[->, btree-line, color=red, line width=2pt]
                (pointer32.south) -- (heap-pointer32.north);

        \end{tikzpicture}
    \end{overprint}
    \end{center}
